Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2022-12-21 paper-1/manuscript.tex
Editing

Across networks and stimuli (Figure \ref{fig2}c), we found that our model reliably produced mismatch responses (t = 11.3, p = 6.7e-21; one-sided t-test for mismatch index > 0, n = 120) while both SSA index (t = 7.84, p = 1.05e-12) and DDI (t = 6.49, p = 1.05e-09) were also positive. The average DDI value reached around 0.1, which was less than the values reported by \cite{Kubota2021-dx}, but note that our target stimuli were presented more frequently (20\%) than theirs (10\%) in the dev and msc sequences.

\begin{figure*}%
    \centering
    \includegraphics{fig3.pdf}
    \caption{}
    \label{fig3}
\end{figure*}
\textbf{Fig. 3} Deviance detection under model ablation. \textbf{a} Sample network responses to target stimulation, with the deviance detection index in each instance noted in the plot titles. The color code is the same as in Figure \ref{fig2}. \textbf{b} SSA indices across all networks and stimuli. Asterisks indicate data greater than 0 at a significance level of p<0.05, see main text for detailed statistics. \textbf{c} Deviance detection indices across all networks and stimuli.

>>>>

Across networks and stimuli (Figure \ref{fig2}c), we found that our model reliably produced positive mismatch responses (t = 11.3, p = 6.7e-21; one-sided t-test, n = 120) while both SSA index (t = 7.84, p = 1.05e-12) and DDI (t = 6.49, p = 1.05e-09) were also positive. The average DDI value reached around 0.1, which was less than the values reported by \cite{Kubota2021-dx}, but note that our target stimuli were presented more frequently (20\%) than theirs (10\%) in the dev and msc sequences.

\begin{figure*}%
    \centering
    \includegraphics{fig3.pdf}
    \caption{}
    \label{fig3}
\end{figure*}
\textbf{Fig. 3} Deviance detection under model ablation. \textbf{a} Sample network responses to target stimulation, with the deviance detection index in each instance noted in the plot titles. The color code is the same as in Figure \ref{fig2}. \textbf{b} SSA indices across all networks and stimuli. Asterisks indicate data greater than 0, established by t-test with significance level 0.05, see main text for detailed statistics. \textbf{c} Deviance detection indices across all networks and stimuli.
